\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-26 Paper.tex
first cuts

\usepackage{titlesec} % Allows customization of titles
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
%\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering\bfseries}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large\scshape}{\thesubsection.}{1em}{} % Change the look of the section titles
\usepackage{cite}
\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Naomi Pentrel $\cdot$ \href{mailto:n.pentrel@jacobs-university.de}{n.pentrel@jacobs-university.de} $\cdot$ \today} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[]{natbib}
\usepackage{tocloft}
\renewcommand*{\figureautorefname}{figure}
\def\stex{\texorpdfstring{\raisebox{-.5ex}S\kern-.5ex\TeX}{sTeX}\xspace}
\def\sTeX{\stex}

@@

@@

\begin{document}
\thispagestyle{empty}
\pagenumbering{roman}
\begin{flushright}
    \includegraphics[scale=1.0]{assets/Logo}
  \end{flushright}
  \vspace{20mm}
  \begin{center}
    \huge
    \textbf{The Combination of Spatial Narrative and Semantic Closeness to Derive Visualizations of Information Graphs}
  \end{center}
  \vspace*{4mm}
  \begin{center}
   \Large by
  \end{center}
  \vspace*{4mm}
  \begin{center}
    \Large
    \textbf{Naomi Pentrel}
  \end{center}
  \vspace*{20mm}
  \begin{center}
    \large
    Bachelor Thesis in Computer Science
  \end{center}
  \vfill
  \begin{flushright}
    \large
    \begin{tabular}{l}

      \hline
      Prof. Dr. Michael Kohlhase \\
      \\
    \end{tabular}
  \end{flushright}
  \vspace*{8mm}
  \begin{flushleft}
    \large
    Date of Submission: \today \\
    \rule{\textwidth}{1pt}
  \end{flushleft}
  \begin{center}
    \Large Jacobs University Bremen - School of Engineering and Science
  \end{center}

\newpage
\noindent
With my signature, I certify that this thesis has been written by me using only the indicated resources and materials. Where I have presented data and results, the data and results are complete, genuine, and have been obtained by me unless otherwise acknowledged; where my results derive from computer programs, these computer programs have been written by me unless otherwise acknowledged. I further confirm that this thesis has not been submitted, either in part or as a whole, for any other academic degree at this or another institution.

  \vspace{20mm}

    \includegraphics[scale=0.2]{assets/Signature}
 \hfill Bremen, \today

@@

 \section*{Abstract}
 \label{sec:abstract}
Visualization of knowledge is important to foster learning. To optimize the visualization of information and its interdependencies, we focus on identifying ways to present information without loosing context. The following research takes an existing annotated corpus and presents its contents in an interactive way that allows the audience to see the dependencies of the covered topics. This form of presenting knowledge enables users to interactively examine materials that are related to the topics the audience is interested in.\\

Taking the typical lecture as an example, it is often the case that, especially towards the end of the semester, students have difficulties remembering earlier topics. When a new topic is introduced it would be ideal to have a simple way to find dependencies and present students with an easy way to catch up.\\

The OMDoc (\textbf{O}pen \textbf{M}athematical \textbf{Doc}uments) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, the implemented system can present different pieces of mathematical concepts in an interactive and connected way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories. Along these lines it examines if and how spatial narrative and semantic closeness can be combined to foster learning. This approach to presenting learning materials changes how we interact with course material which will allow students to learn better. Ultimately, this research is applicable to almost all areas in which knowledge needs to be transferred.\\

\newpage
\tableofcontents

\clearpage

\newpage
\thispagestyle{empty}
\topskip0pt
\vspace*{\fill}
\begin{center}
\textsc{Aut viam inveniam aut faciam}\\

\vspace*{1cm}

\textit{(I'll either find a path or make one)}\\

\vspace*{4cm}

\centering

\begin{quoting}
\begin{center}
\noindent
\textit{At this point, I would like to thank Prof. Dr. Michael Kohlhase for being an inspiring and helpful supervisor. Additionally, I would like to thank Mihnea Iancu and Tom Wiesing for aiding me in my research project.\\}
\end{center}
\end{quoting}

\vspace*{\fill}
\end{center}

\newpage
\pagenumbering{arabic}

@@

Learning new things is a bit like hiking up a mountain. If you have ever gone hiking, you know that it is relatively hard to hike up a steep mountain directly as shown in \autoref{fig:straight}. Some people do it but most people will rather hike up as shown in \autoref{fig:curvy}. Both paths lead to the goal. Within education, there is normally only one straight path. That is true for the narration in books, movies, and also traditional slide-based presentations. This has not changed in decades. With the advancement of technology, we are however able to change the way presentations and their narratives work. We can make it possible to link content that logically belongs together, in other words, content that is semantically close. Through the linking of content it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined straight path, but rather along the path that allows the audience to take small detours and ultimately make the most out of the presentation.\\

This idea of linking content is not new. When Tim Berners-Lee laid out his Semantic Web Roadmap \cite{BernersLee:tsw98}, its intention was to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources. Both the semantic web and the research at hand strive to connect pieces of information through adding context and thus to not just provide information, but rather knowledge. Within presentations, the intention is to present information in an interconnected way that provides context and thus facilitates understanding and learning.\\

@@

Annie's example shows the dependencies of different pieces of information (see \autoref{fig:deppyg}), i.e. the Pythagorean theorem depends on knowledge of area calculation, lengths, squares, right angles, and angles. As Annie and many of us who have witnessed many presentations know, traditional slide-based presentations lack the connectivity and flexibility to allow us to directly look related topics up. By adding connectivity and flexibility, we would allow Annie to not just look up the prerequisite knowledge such as what right angles are but hopefully also to understand the Pythagorean theorem.\\

@@

\section{Related Work}
\label{sec:relatedworks}

When searching for related work there is little to be found. Some works have focused on making teaching more effective by providing students with all lecture materials directly after class which has been found to have a positive influence on learning \cite{DBLP:dblp_journals/tochi/BrothertonA04}. For this purpose, systems that can automatically capture and index classroom events as videos and images have been devised \cite{indexedclass:npentrel14}. Some of these systems use temporal information \cite{DBLP:dblp_journals/isci/ChungS97} to show multiple resources in sync as they appeared in the lecture. However, while this approach also aims at improving the learning experience, it does not in any way link content semantically based on dependencies or allow for more interactive presentations through combining semantic closeness and spatial narrative.\\

Another piece of research has focused on the automatic generation of mind maps from text \cite{abdeen2009direct}. The software they developed uses Semantic Web technologies to create mind maps that show the relations between nodes that represent different objects. While the research at hand also intends to show the relation between pieces of information, it does it on a different level. For instance, it can represent that Shakespeare lived in Stratford but it would not be able to show the dependencies of mathematical concepts as it is limited to representing nodes in single words within the mind map. This research, on the other hand, will focus on exactly that, i.e. dependencies and the creation of interactive presentations.\\

There has also been research focusing on guided tours in mathematics \cite{SieBen:acgap00}. This creates guided tours on topics depending on the background of the user. While working towards the same goal, namely to improve knowledge transfer, it differs from this work in its presentation format. While Siekmann et al., focused on one topic and displaying it differently to users with different backgrounds, this research will show the topics of a whole course while allowing to see dependencies and while allowing to diverge from the prescribed presentation path.\\

Adding on to the research about guided tours in mathematics, there has also been research on semantic document navigation \cite{Koh:NavigationInMathDocs2012}. It demonstrates the need for assistance in form of navigation support for the reading of mathematical documents by creating a system that allows for semantic navigation in Excel spreadsheets. This research underlines the importance of a system that allows users like Annie to navigate information according to dependencies.

\section{Preliminaries}
\label{sec:preliminaries}

In the following we will examine some prerequisite knowledge. By engaging with our example presentation we will show how the presentation can be improved to transfer knowledge more effectively.

\subsection{Terminology}
\label{sec:terminology}

Before discussing the buzzword knowledge transfer further, we will first engage in the conceptualization of the terms \textit{information}, \textit{knowledge}, and \textit{context}.\\

The Oxford Dictionary of English \cite{OED:npentrel14} defines \textit{information} as "what is conveyed or represented by a particular arrangement or sequence of things". Recalling \autoref{fig:slideP} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}. For the term \textit{knowledge}, we will use the definition in Merriam-Webster's thesaurus \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association". This \textit{association} is of special importance for the current project. We will define it as knowledge that is made up out of several pieces of information that are connected. In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see \autoref{fig:deppyg} above).\\

According to the Merriam-Webster thesaurus \cite{Webster:npentrel14}, \textit{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning". Context can be easily explained with the example of Annie learning the Pythagorean theorem. The \textit{information} about the calculation of the length of the third side of the triangle is only helpful for Annie within the \textit{context} of the pieces of \textit{information} this depends on. Without this \textit{context}, Annie cannot understand the theorem. Figure \ref{fig:deppyg} above illustrates the context by showing the dependencies of the theorem, i.e. calculating squares, area calculation, triangles, and right angles. It represents relatedness of \textit{concepts} by linking the different \textit{concepts} with lines, thus creating \textit{associations} between the different pieces of \textit{information}. The relatedness between the relevant concepts can also be imagined as a network. We will be using the terms \textit{context} and \textit{network} almost interchangeably and depend on the reader to have the right intuition about these terms.

\subsection{OMDoc}
\label{sec:OMDoc}

OMDoc \cite{Kohlhase:OMDoc1.2} is an XML-based system that provides a data model and a format for content markup for mathematical documents. As such it is a semi-formal domain ontology. An ontology provides the framework for creating a semantic structure. It formally describes concepts within a specified area. A semi-formal ontology \cite{Sheth:npentrel14} is an ontology where formality of semantics is not a given. The semi-formal ontology can consist of partial or incomplete knowledge. \\

If OMDoc was used in every part of mathematics (and related fields), we would have a repository of mathematical knowledge that could be processed in various ways. This is possible because OMDoc provides the framework to create and store mathematical objects such as definitions and concepts. The relations between different mathematical objects and the attributes of mathematical objects can be added through annotations. This elevates the net of separate pieces of information that are stored individually to a semantic representation and can be used to improve knowledge transfer.

\subsection{Status of Information within the (Dis)Course}
\label{sec:infostatus}

In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed. Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information. \textit{Familiar/ old} information is shared by speaker and addressee, i.e. it is in the intersection of knowledge of student and teacher. \textit{New/ unfamiliar} information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}. In addition, one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.

\subsection{Primitives}
\label{sec:primitives}

Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness. Primitives are the different elements of representation. In terms of evaluation it is important to have intuitive primitive elements. The primitive elements can be further subdivided into structural and semantic primitives \cite{DBLP:dblp_conf/acl/Salveter80}. The structural primitives have little inherent semantics associated with them whereas the semantic primitives carry meaning.\\

Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter. When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations to add information or to show what kind of a relation it is. In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate. Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to \autoref{fig:deppyg}). These structural primitives and semantic primitives provide the basics that information graphs can be built on.\\

For impress.js, the primitive elements are text, images, slides, and the visual relation between the different slide-like structures. The slides can be mapped directly to the nodes/concepts which graphs use. Text and images are taken for granted within the slides. Similarly, the visual relation between different slides is very much like the relations between nodes. However, the relations can be much more expressive within impress.js.\\

These relations or connections between different slides do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another. As such the temporal associations show the path that a traditional lecture would take. The dependencies that are visualized around each slide, mainly above or below the slide, allow for additional interactivity.

\subsection{Spatial Narrative}
\label{sec:spatialnarrative}

The development of presentation tools like impress.js and Prezi, has changed how people think about presentations while making use of spatial narrative. Prezi is "a virtual whiteboard that transforms presentations from monologues into conversations: enabling people to see, understand, and remember ideas" \cite{Prezi:npentrel14}. When doing a good prezi presentation one has to understand the topic one is presenting on a deeper level and think about how one can portray connections between content visually.\\

The concept of Spatial Narrative stems from the establishment of frameworks for "the creation of computer-assisted flexible \textit{guided tours} based on the thematically and narrative linking of a set of locations within an area into a \textit{spatial narrative}" \cite{SpatialNarratives:npentrel14}. Teachers that are presenting a topic are an example for the experience of a tour guide for a certain topic.\\

The benefit of spatial narrative is that the audience gains a more thorough understanding of the subject and has a better understanding of the interconnections between different pieces of information. By providing the audience with a story as a narrative one also makes use of the concept of Storytelling which is largely accredited with the benefit that the audience will have an easier time following the presenter. That is the case because our brains are not made to memorize a lot of unconnected pieces of information; it is far easier for us to remember information if it comes in story form \cite{Storytelling:npentrel14}.\\

\begin{wrapfigure}{r}{0.45\textwidth}
\vspace{-28pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.43 \textwidth]{assets/final/arrowsPyth}
    }
  \end{center}
\vspace{-20pt}
  \caption{Connection of Slide}
  \label{fig:arrowspyg}
\vspace{-10pt}
\end{wrapfigure}

In this research we will use this knowledge to form an interconnected network of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge. For Annie this means that she will be presented with the \textit{course-new} information about the Pythagorean theorem in a way that the dependent \textit{course-ancient} and \textit{course-old} information would be visually close and visually connected (see figure \ref{fig:arrowspyg}). It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in an instant.

\subsection{impress.js}
\label{sec:Impressjs}

For the implementation of \sys, impress.js will be used, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations. The open-source presentation framework \textbf{impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka. It combines HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers. The presentation data is entered in the HTML file; each slide in its own div with \texttt{data-x}, \texttt{data-y}, and \texttt{data-z} attributes to change the position of the slide. The \texttt{data-x} and \texttt{data-y} attributes change the position of the element according to the normal x- and y-axes. The \texttt{data-z} attribute changes the closeness of the elements along the z-axis.\\
\definecolor{bg}{rgb}{0.90,0.90,0.90}

\begin{wrapfigure}{r}{\textwidth}
\vspace{-0pt}
\begin{minted}[linenos=true, bgcolor=bg]{C}
<div class="step" data-x="1000" data-y="0">
  Slide Content
</div>
\end{minted}
\vspace{-8pt}
  \caption{Code Snippet to Create a Slide}
  \label{fig:SSlide}
  \vspace{12pt}
\end{wrapfigure}

\begin{wrapfigure}{r}{0.3\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.28 \textwidth]{assets/rotate}
    }
  \end{center}
\vspace{-20pt}
  \caption{Rotations \cite{Rotations:npentrel14}}
  \label{fig:Rotate}
\vspace{-10pt}
\end{wrapfigure}

Apart from these basic attributes, impress.js offers the \texttt{data-scale} attribute to scale content, making slides appear bigger or smaller, and the \texttt{data-rotate} attribute which rotates slides in 3 dimensions using \texttt{data-rotate-x}, \texttt{data-rotate-y}, and \texttt{data-rotate-z}. As shown in \autoref{fig:Rotate} this allows the presentation to go into the third dimension.\\

In the following code snippets, a few other basic functionalities are illustrated \cite{andismith:npentrel15}. The opacity attribute allows us to discriminate between active and inactive slides which allows us to hide content so as not show too much information to a user at once. Adding an overview can be accomplished with the last part of the CSS snippet and the HTML snippet below that.

\begin{wrapfigure}{l}{\textwidth}
\vspace{0pt}
\begin{minted}[linenos=true, bgcolor=bg]{C}
.step { opacity: 0.2; }
.step.active { opacity: 1; }
.step-overview .step { opacity: 1; cursor: pointer; }
\end{minted}
\vspace{-8pt}
  \caption{Code Snippet to Show and Hide Content}
  \label{fig:SSlide}
  \vspace{20pt}
\end{wrapfigure}

\begin{wrapfigure}{l}{\textwidth}
\vspace{-10pt}
\begin{minted}[linenos=true, bgcolor=bg]{C}
<div id="overview" class="step" data-x="8000" data-y="1000" data-scale="10">
</div>
\end{minted}
\vspace{-11pt}
  \caption{Code Snippet for an Overview}
  \label{fig:SSlide}
  \vspace{12pt}
\end{wrapfigure}

To link back to a slide, slides are accessible via IDs. The slide with the ID \texttt{conclusion} will thus be accessible by appending \texttt{\#/conclusion} to the end of the URL.

@@

Building on the preliminaries, we will now commence the journey towards building a more effective presentation format to improve knowledge transfer by allowing flexibility in presentations. To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created.\\

@@

To bring the presentation to life the library impress.js which was introduced in \autoref{sec:Impressjs} is used because it makes it simple to reuse the XHTML code that was automatically generated by lmh. An important additional reason for the choice of impress.js \cite{JSImpress:npentrel14} is that it enables us to use spatial Narrative as discussed in \autoref{sec:spatialnarrative} and \autoref{sec:Impressjs}. The library impress.js works in all modern browsers that support CSS 3D transforms; some older and mobile browsers are, however, not able to display the created presentations properly.

@@

The most interesting movement is the rotations. It should be briefly mentioned that too much rotation leads to seasickness in users, as anyone who has seen a bad prezi can attest to. These are generally rotations around the x-axis that rotate more than 20\degree. Since we only rotate around the y-axis, our rotations are not affected. Instead of causing seasickness, our rotations aim to give the viewer the feeling of entering a topic and a different storyline. Thus entering a different topic comes with a change of perspective which is underlined by the 3D transformation that the user sees. Overall, these movements add expressiveness to the relations and allow for intuitive interaction with the presentation. \footnote{To see the presentation in action visit: \href{http://npentrel.github.io/pythagoreantheorem.html\#/overview}{http://npentrel.github.io/pythagoreantheorem.html\#/overview}}\\

@@

\section{Future Work and Possible Extensions}

This section lists some ideas on future work regarding this topic and the created system \sys. Before embarking on improvements of the system, a qualitative and quantitative analysis of the produced visual presentations should be conducted to confirm that this system aids users in understanding content better. For the quantitative analysis it would be ideal to take a course that has already been taught using a more traditional approach to presentations which can then function as a control group. After teaching the whole course using the newly created presentations, the data of how the students in this test group performed can be compared with the gathered data from how students used to perform in the course. For a qualitative analysis, students who have been subject to the use of and who have actively used the new presentation could be interviewed.\\

Apart from an analysis to evaluate the effectiveness of the created presentations, the whole system could be made more user friendly for both the creator and the users of the presentations. By improving the creation user interface and allowing for users to choose their own designs, it becomes easier to use and more attractive for users. Adding an editor would make \sys more user friendly for creators as well. To change a presentation after it has been created, a user currently has to understand how to manipulate HTML, JavaScript, and also CSS.\\

In terms of improving the usability for the users that will view and interact with the presentations, one could try to find a way to make use of relative size to additionally convey importance using impress.js' \texttt{data-scale} attribute. This would further add more semantic meaning to the slides. Additionally, one could think about adding a progress bar by using the work of Matthias Bilger \cite{bilger:npentrel15} to motivate users to continue.\\

Overall it is even thinkable to create a different version of this system that could be made available to general users outside this research domain. The idea would be to allow users to add slides in an editor and to allow them to add dependencies themselves. Possibly the system could even suggest dependencies. As an example, I could very well envision a biology presentation that explains photosynthesis and allows the attentive student to catch up on dependencies such as the process that transforms ADP to ATP.\\

In terms of improving content, it would be interesting to not just provide paths to dependencies or prerequisite knowledge but also to knowledge that builds on the current topic. That way students that learn fast can already explore higher levels.\\

This whole research project might also benefit from machine learning which could allow us to suggest likely dependencies. On an individual basis we could use it to learn what the user knows and what the user does not know. Ideally we do not always want to show very low level dependencies, such as how to multiply, which our system could then learn. Combining machine learning with the identification of more didactic paths or figures within the data such as the example in \autoref{fig:pathExample} could further improve knowledge transfer.

@@

This relational presentation combines spatial narrative with information about the relations between different pieces of information into a visual information graph. In doing so it creates presentations that use meaningful visual connections between pieces of information to allow for intuitive interaction with the presentation. This allows Annie choose her own path in going through the presentation while seamlessly looking up related information.\\

The benefits are not just for Annie when she is going through the presentation on her own, though, Annie's teacher now has a tool that allows him to use his normal lecture material in a more interactive way. Thus when the teacher realizes that the students need to revise previous material, the teacher can seamlessly go to that material and provide them with a good learning experience. This facilitates knowledge transfer and allows for a more engaging and interactive education.\\

@@

>>>>

\usepackage{titlesec} % Allows customization of titles
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
%\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering\bfseries}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large\scshape}{\thesubsection.}{1em}{} % Change the look of the section titles
\usepackage{cite}
\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{\href{mailto:npentrel@gmail.com}{Naomi Pentrel} $\cdot$ \href{mailto:m.kohlhase@jacobs-university.de}{Michael Kohlhase} $\cdot$ \today} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[]{natbib}
\usepackage{tocloft}
\renewcommand*{\figureautorefname}{figure}
\def\stex{\texorpdfstring{\raisebox{-.5ex}S\kern-.5ex\TeX}{sTeX}\xspace}
\def\sTeX{\stex}

@@

\definecolor{bg}{rgb}{0.90,0.90,0.90}

@@

\begin{document}
\thispagestyle{empty}
\pagenumbering{roman}
\begin{flushright}
    \includegraphics[scale=1.0]{assets/Logo}
  \end{flushright}
  \vspace{20mm}
  \begin{center}
    \huge
    \textbf{Relational Presentation Using Semantic Closeness}\\
    \vspace*{2mm}
	\Large
	\textbf{-\\Spatial Narrative for Mathematical Content}
  \end{center}
  \vspace*{2mm}
  \begin{center}
   \Large by
  \end{center}
  \vspace*{4mm}
  \begin{center}
    \Large
    \textbf{Naomi Pentrel\\ \& \\ Prof. Dr. Michael Kohlhase}
  \end{center}
  \vspace*{4mm}
  \begin{center}
    \large
  \end{center}
  \vfill
  \begin{flushright}
    \large
    \begin{tabular}{l}      
      \\
    \end{tabular}
  \end{flushright}
  \vspace*{0mm}
  \begin{flushleft}
    \large
    Date of Submission: \today \\
    \rule{\textwidth}{1pt}
  \end{flushleft}
  \begin{center}
    \Large Jacobs University Bremen - School of Engineering and Science
  \end{center}

@@

 \section*{Abstract}
 \label{sec:abstract}
Visualization of knowledge is important to foster learning. Especially so in Mathematics where students have to understand not just one topic at a time but also the related concepts. To optimize the visualization of information and its interdependencies, a way to present information without loosing context is necessary. The following research takes an existing annotated corpus and presents its contents in an interactive way that allows the audience to see the dependencies of the covered topics. This form of presenting knowledge enables users to interactively examine materials that are related to the topics the audience is interested in.\\

Taking the typical Mathematics lecture as an example, it is often the case that students have different backgrounds. Some might have learned linear algebra while other have not yet. Additionally, especially towards the end of the semester, students often have difficulties remembering earlier topics. When a new topic is introduced it would therefore be ideal to have a simple way to find dependencies and present students with an easy way to catch up.\\

The OMDoc (OpenMathematical Documents) format is a content markup scheme for mathematical documents. Using OMDoc, the proposed system can present different pieces of mathematical concepts in an interactive and connected way that allows students to learn the concepts the current topic depends on by taking a small detour through those topics, should they need to refresh their memories. Along these lines it examines if and how spatial narrative and semantic closeness can be combined to foster learning. This approach to presenting learning materials changes how we interact with course material which will allow students to learn better. Ultimately, this research is applicable to almost all areas in which knowledge needs to be transferred.\\

\newpage
%\tableofcontents

%\clearpage

%\newpage
%\thispagestyle{empty}
%\topskip0pt
%\vspace*{\fill}
%\begin{center}
%\textsc{Aut viam inveniam aut faciam}\\

%\vspace*{1cm}

%\textit{(I'll either find a path or make one)}\\

%\vspace*{4cm}

%\centering

%\vspace*{\fill}
%\end{center}

%\newpage
\pagenumbering{arabic}

@@

Learning new things is a bit like hiking up a mountain. If you have ever gone hiking, you know that it is relatively hard to hike up a steep mountain directly as shown in \autoref{fig:straight}. Some people do it but most people will rather hike up as shown in \autoref{fig:curvy}. Both paths lead to the goal. Within Mathematics classes, there is normally only one straight path and this has not changed in decades. With the advancement of technology, we are however able to change the way presentations and their narratives work. We can make it possible to link content that logically belongs together, in other words, content that is semantically close. Through the linking of content it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined straight path, but rather along the path that allows the audience to take small detours and ultimately make the most out of the presentation.\\

@@

Annie's example shows the dependencies of different pieces of information (see \autoref{fig:deppyg}), i.e. the Pythagorean theorem depends on knowledge of area calculation, lengths, squares, right angles, and angles. As Annie and many of us who have witnessed many presentations know, traditional slide-based presentations lack the connectivity and flexibility to allow us to directly look related topics up. However, especially in mathematics, students would benefit from the possibility to take detours through half-forgotten topics. By adding connectivity and flexibility, we would allow Annie to not just look up the prerequisite knowledge such as what right angles are but hopefully also to understand the Pythagorean theorem.\\

@@

@@

We will now commence the journey towards building a more effective presentation format to improve knowledge transfer in Mathematics by allowing flexibility in presentations. In the following we will assume the reader is familiar with OMDoc \cite{Kohlhase:OMDoc1.2} and with the open-source presentation framework \textit{impress.js} \cite{JSImpress:npentrel14} which will be used to create the final presentation in the form of an interconnected network of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge. To create these presentations automatically, the tool \sys \cite{npentrel:npentrel15} was created. \\

@@

To bring the presentation to life the library impress.js is used because it makes it simple to reuse the XHTML code that was automatically generated by lmh. An important additional reason for the choice of impress.js \cite{JSImpress:npentrel14} is that it enables us to use spatial narrative. The library impress.js works in all modern browsers that support CSS 3D transforms; some older and mobile browsers are, however, not able to display the created presentations properly.

\subsection{Status of Information within the (Dis)Course}
\label{sec:infostatus}
\ednote{not sure where to put this}
In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed. Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information. \textit{Familiar/ old} information is shared by speaker and addressee, i.e. it is in the intersection of knowledge of student and teacher. \textit{New/ unfamiliar} information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}. In addition, one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.

\ednote{For Annie this means that she will be presented with the \textit{course-new} information about the Pythagorean theorem in a way that the dependent \textit{course-ancient} and \textit{course-old} information would be visually close and visually connected (see figure \ref{fig:arrowspyg}). It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in an instant.}

@@

The most interesting movement is the rotations. It should be briefly mentioned that too much rotation leads to seasickness in users, as anyone who has seen a bad prezi can attest to. These are generally rotations around the x-axis that rotate more than 20\degree. Since we only rotate around the y-axis, our rotations are not affected. Instead of causing seasickness, our rotations aim to give the viewer the feeling of entering a topic and a different storyline. Thus entering a different topic comes with a change of perspective which is underlined by the 3D transformation that the user sees. Overall, these movements add expressiveness to the relations and allow for intuitive interaction with the presentation. \footnote{To see the presentation in action visit: \href{http://npentrel.github.io/pythagoreantheorem.html\#/overview}{http://npentrel.github.io/pythagoreantheorem.html\#/overview}.}\\

@@

@@

This relational presentation combines spatial narrative with information about the relations between different pieces of information into a visual information graph. In doing so it creates presentations that use meaningful visual connections between pieces of information to allow for intuitive interaction with the presentation. This allows Annie to choose her own path while going through the presentation and seamlessly looking up related information.\\

The benefits are not just for Annie when she is going through the presentation on her own though, Annie's teacher now has a tool that allows him to use his normal lecture material in a more interactive way. Thus when the teacher realizes that the students need to revise previous material, the teacher can seamlessly go to that material and provide them with a good learning experience. This facilitates knowledge transfer and allows for a more engaging and interactive education.\\

@@

To conclude, I leave the reader to ponder how much education would change if we could allow individuals to learn at their own pace following their own path and easily learning course-ancient information in guided tours. \sys definitely helped Annie and I strongly believe that the mentioned benefits would benefit all of us, whether in the role of the presenter or in the role of the viewer.
